Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-09-07 article.tex
added reference to reduced basis function paper
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1374 ccdd05d5-56c1-461a-bf98-85f6876523b4

Fortunately, the morphology of inspiral signals can be exploited to offset some
of the computational complexity of low-latency algorithms.  First, the signals
evolve slowly in frequency, so that they can be broken into contiguous
band-limited time intervals and processed at possibly lower sample rates.
Second, inspiral filter banks consist of highly similar templates, admitting
methods such as singular value decomposition (\SVD) to reduce the number of
templates \citep{Cannon:2010p10398}. We will use both aspects to demonstrate
that a very low latency detection statistic is possible with current computing
resources.  Assuming the other technical sources of latency can be reduced
significantly, this could make it possible to send prompt alerts to the
astronomical community.

>>>>

Fortunately, the morphology of inspiral signals can be exploited to offset some
of the computational complexity of low-latency algorithms.  First, the signals
evolve slowly in frequency, so that they can be broken into contiguous
band-limited time intervals and processed at possibly lower sample rates.
Second, inspiral filter banks consist of highly similar templates, admitting
methods such as the singular value decomposition (\SVD)~\citep{Cannon:2010p10398}
or the Gram-Schmidt process~\citep{rbf} to reduce the number of templates.  We
will use both aspects to demonstrate that a very low latency detection statistic
is possible with current computing resources.  Assuming the other technical
sources of latency can be reduced significantly, this could make it possible to
send prompt alerts to the astronomical community.
